 %Your abstract in English. Try to keep the abstract short, approximately 
 %100 words should be enough. Abstract explains your research topic, 
 %the methods you have used, and the results you obtained. 
This master's thesis studies the effects of a slotless, continuous metal cover of a mobile terminal on the performance of its antennas. Additionally, LTE MIMO antennas are designed together with GPS and Wi-Fi antennas. The cellular antennas should operate on $704$--$960\,\mega\hertz$ and $1.71$--$2.69\,\giga\hertz$ with at least 30\,\% efficiency, and the other antennas at 1.575\,GHz, 2.4\,GHz, and 5\,GHz bands with 40\,\% efficiency. \\

The topic is studied by completing electromagnetic simulations. The used model of the mobile phone is much more accurate than the ones used in earlier studies. The simulations focus on the antenna structures, locations, and sizes, as well as feeding of them. Additionally, matching circuits are investigated, and designed for each antenna. The effect of the metal cover is studied with several test cases, each of which focuses on one parameter, e.g.\ a dimension, location, or feed of the antenna. \\

The first simulations are done with a simple model, and a concept for the cellular antennas is constructed on the basis of the obtained results. The final simulations are completed, and the antennas optimized with the accurate model. The proposed structure consists of three closely located, strongly coupling elements. The cellular antennas are at distinct ends of the device, and integrated into the side metals. GPS and Wi-Fi antennas are also integrated into the sides, and placed in the area between the ends of the phone. \\

The main challenge due to the metal-cover is obtaining sufficient and wideband matching. Regardless the challenging environment, all the designed antennas fulfill their requirements. Based on the results, achieving a good antenna performance in a metal-covered phone is not impossible.