%\mysection{Esipuhe}
\mysection{Preface}
{\parindent0pt
This master's thesis is the last piece of a puzzle called my studies. The last five months that I have used for this thesis are only a small portion of them. The past seven years have been one great experience, of which I regret nothing.\\

Since my time as a degree student is coming to an end, I would like to express my gratitude to several people. First, I would like to thank the supervisor of my thesis, Prof.\ Ville Viikari, for giving me the opportunity to work in his research group and study this interesting topic, for his constructive feedback, and for letting me work independently. This thesis is a part of a larger research project with AAC Technologies to whom I am thankful for funding this project. I am also grateful to my advisor, D.Sc.\ (Tech.) Anu Lehtovuori, for the discussions with her every day that inspired to look things differently, developed my thinking, and helped to finalize this thesis. Without her comments the contents of this thesis would have been a lot more challenging to digest.\\

During my time in Otaniemi, I have met more new people than I can count, and some of them will remain very good friends of mine. I would like to bring up two very important persons. Joel and Mikko have had a significant impact on my study time, and also have supported me a lot during the writing of this thesis, while they have been working on their own theses. Thank you. Friendships are not limited to individuals. I have been a member of so many wonderful groups during the years. Without them my study time would have been very boring. So thank you SIKH14, SIKH013, FTMK13, Neuvosto'14, HTMK12, SIK-fuksit13, EST~IX, Tempaus2016 team, and Polytechnical Students' Museum.\\

The most supportive group without any questions is my family: mother Sirpa, father Matti, and little sisters Saila and Niina. For all my life, they have given me the freedom to do my own choices, of course asking to think twice about the strangest decisions. \\

Last but definitely not least, I would like to thank my beloved Anni, who deserves the sincerest gratitude, for her warmth, support, and understanding during this project, together with the weird moments that constantly cheer me up. \\

I hope the future students will enjoy their studies as much as I have. Jappadaida and Iuvenis in Aeternum!}

\vspace{2cm}
Tekniikan kehdossa, 4.10.2016

\vspace{5mm}
{\hfill Joni Kurvinen \hspace{1cm}}